Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-18 paper/manuscript.tex
Added a sentence to methods

@@

\subsection*{H3 sequence numbering}
Unless otherwise indicated, all residues are numbered in H3 numbering in this paper, with the signal peptide in negative numbers, the HA1 subunit as plain numbers, and the HA2 subunit denoted with "(HA2)". We converted the sequential residue numbers into H3 numbering by running the Python script available on \url{https://github.com/jbloomlab/HA_numbering}. In this script, we used MUSCLE to align the WSN/1933 H1 HA sequence to the 4HMG pdb sequence for the A/Aichi/2/1968 H3 HA, which allowed us to convert from the sequential numbering to the H3 numbering scheme.

@@

\subsection*{Data availability and source code}
Deep sequencing data are available from the Sequence Read Archive under BioSample accession (\comment{add this}).

>>>>

For the cladogram in Figure~\ref{fig:structures}C, the amino-acid identities at site 38 are from the strains tested against C179 in~\cite{dreyfus2013structure}. For subtypes not tested, we used the identity from the corresponding strain listed above.

@@

\subsection*{H3 sequence numbering}
Unless otherwise indicated, all residues are numbered in H3 numbering in this paper, with the signal peptide in negative numbers, the HA1 subunit as plain numbers, and the HA2 subunit denoted with "(HA2)". We converted the sequential residue numbers into H3 numbering by running the Python script available on \url{https://github.com/jbloomlab/HA_numbering}. In this script, we used MUSCLE to align the WSN/1933 H1 HA sequence to the 4HMG pdb sequence for the A/Aichi/2/1968 H3 HA \comment{cite Weis1990JMB}, which allowed us to convert from the sequential numbering to the H3 numbering scheme.

@@

\subsection*{Data availability and source code}
Deep sequencing data are available from the Sequence Read Archive under BioSample accession SAMN05789126.
